The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
9.3 release

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
    Marc Fehling,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.3, 2021},
}

@@

\author[4]{Timo~Heister}
 \affil[4]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{tcleven/heister@clemson.edu}}}

@@

% \author[12]{Reza Rastak}
% \affil[12]{Department of Civil and Environmental Engineering,
%   Stanford University,
%   Stanford, CA 94305, USA.
%   {\texttt{rastak@stanford.edu}}}

% \author[**13]{Ignacio Tomas}
% \affil[13]{Sandia National Laboratories, Org 1442,
% P.O. Box 5800, MS 1320, Albuquerque, NM, 87185-1320,
%   \texttt{itomas@sandia.gov}}

\author[1*]{Bruno~Turcksin}
%

%\author[14]{Zhuoran Wang}
%\affil[14]{Department of Mathematics, Colorado State University, Fort Collins,
%          CO 80523-1874, USA.
%{\texttt{zhrwang@math.colostate.edu}}}

@@

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Bruno Blais,
Michele Bucelli,
Marcus Calhoun-Lopez,
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Uwe K\"ocher,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Sebastian Proell,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Konrad Simon,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan,
Jiaqi Zhang.

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Marc Fehling,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells,
    Jiaqi Zhang
  },
  pdftitle={The deal.II Library, Version 9.3, 2021},
}

@@

\author[4]{Timo~Heister}
 \affil[4]{School of Mathematical and Statistical Sciences,
   Clemson University,
   Clemson, SC, 29634, USA
   {\texttt{heister/jiaqi2@clemson.edu}}}

@@

\author[1*]{Bruno~Turcksin}

@@

\author[4]{Jiaqi~Zhang}

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
%      sorted by WB 5/28
Pasquale Africa,
Tyler Anderson,
Mathias Anselmann,
Arpit Babbar,
Maximilian Bergbauer,
Nicolas Barnafi,
Bruno Blais,
Michele Bucelli,
Marcus Calhoun-Lopez,
Praveen Chandrashekar,
Conrad Clevenger,
David F. Castellanos,
Andrew Davis,
Elias Dejene,
Niklas Fehn,
Menno Fraters,
Ivan Fumagalli,
Daniel Garcia-Sanchez,
Rene Gassmoeller,
Nicola Giuliani,
Krishnakumar Gopalakrishnan,
Alexander Grayver,
Olivier Guevremont,
Jake Harmon,
Graham Harper,
Uwe K\"ocher,
Katharina Kormann,
Christoph Kammer,
Wenyu Lei,
Zhou Lei,
Phillip Mobley,
Nils Much,
Pratik Nayak,
Toni El Geitani Nehme,
Justin O'Connor,
Daniel Paukner,
Sebastian Proell,
Lei Qiao,
Ce Qin,
Reza Rastak,
Julian Roth,
Laura Prieto Saavedra,
Doug Shi-Dong,
David Schneider,
Magdalena Schreter,
Richard Schussnig,
Konrad Simon,
Dominic Soldner,
Simon Sticko,
Malhar Tidke,
Ignacio Tomas,
Peter Westerbaan.
